---
title: 'Statistical Inference: Project - Part 1'
author: "Piotr Brdeja"
date: "Sunday, January 25, 2015"
output: html_document
---


####Overview
In this project we had to investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. We have set lambda = 0.2 for all of the simulations. We investigated the distribution of averages of 40 exponentials. 

####Simulations
We had to simulate 1000 averages of 40 observations drawn from the exponential distribution.
The code is as follows:

```{r}
set.seed(1)
lambda <- 0.2
numSim <- 1000
sampleSize <- 40

#Simulating data
data = NULL
for (i in 1 : 1000){
      data = c(data, mean(rexp(40, rate = lambda)))
}
```


```{r, echo=FALSE}
data <- as.data.frame(data)
colnames(data) <- "avarage"

#Creating theoretical distibution
xfit <- seq(min(data), max(data), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(sampleSize)))

#Creating histogram of avarages

library(ggplot2)
g <- ggplot(data, aes(avarage)) + 
      xlab(NULL) + ylab("Density") + 
      ggtitle("Distribution of avarages drawn from \nexponential distribution with lambda = 0.2")

g + 
      geom_histogram(aes(y = ..density..), binwidth = density(rowMeans(x = data))$bw, fill = "white", colour = "black") + 
      geom_density(colour = "black", size = 1) + 
      geom_vline(xintercept = 5, colour = "red", size = 1) +
      geom_vline(xintercept = mean(data$avarage), colour = "black", size = 1) +
      geom_path(data = as.data.frame(yfit), x = xfit, y = yfit, colour = "red", linetype = 2, size = 1)
```

```{r, echo=FALSE}
qqnorm(data$avarage); qqline(data$avarage)
```

####Sample Mean versus Theoretical Mean
The theoretical sample mean is centered at lambda^-1 = **5** and the distribution of sample means is centered at mean **4.9900**. 


####Sample Variance versus Theoretical Variance
The variance of sample means is **0.6111** where the theoretical variance of the distribution is 2/n = 1/(2n) = 1/(0.04 × 40) = **0.625**.


####Distribution


This chart from above suggests the normality of distribution according to the Central Limit Theorem. Additionally we can run **Shapiro-Wilk** test, which checks whether or not the distribution is normal, but it **was not in the lectures**. This test shows us that our data is not normally distributed with alfa = 0.05 and p-value = 0.00025.

```{r}
shapiro.test(data$avarage)
```