---
title: 'Statistical Inference: Project - Part 2'
author: "Piotr Brdeja"
date: "Sunday, January 25, 2015"
output: html_document
---


####Overview
The analysed data set contains the response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).
```{r}
head(ToothGrowth)
```


####Basic exploratory analysis
```{r, echo=FALSE}
library(datasets)
library(ggplot2)
ggplot(data = ToothGrowth, aes(x = as.factor(dose), y = len, fill = supp)) + 
      geom_bar(stat = "identity") + 
      facet_grid(. ~ supp) + 
      labs(x = "Dose [mg]", y = "Tooth length", title = "ToothGrowth Dataset") + 
      guides(fill = guide_legend(title = "Delivery method"))
```

It is very easy to notice that dose of the Vitamin C has an impact on the tooth length of guinea pigs. It's unclear which delivery method is better. For this we need to verify hypothesis and find out which delivery method is better.


####Summary
```{r}
summary(ToothGrowth)
```


####Tooth growth by supp and dose comparison
```{r}
OJ <- ToothGrowth[ToothGrowth$supp == "OJ",]
VC <- ToothGrowth[ToothGrowth$supp == "VC",]
t.test(x = OJ$len, y = VC$len)
```
The null hypothesis states that the delivery method has no impact on tooth growth. The alternative hypothesis says that true difference in means is not equal to 0, hence one method is better than the other. With results from the above and p-value = 0.06063 with alfa = 0.05 we fail to reject the null hypothesis. 