---
title: "Practical Machine Learning"
author: "Prediction Assignment Writeup"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. 

## Data

In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: `http://groupware.les.inf.puc-rio.br/har`.

## Cleaning data

1. The first thing to do was loading the data. Thist step required multiple iterations and every csv loading was followed by examining data. After several trials a good combination of NAs falues was found.

```{r, eval=FALSE}
dataTrain <- read.csv("data/pml-training.csv", na.strings = c("", "NA", "#DIV/0!"))
dataTest <- read.csv("data/pml-testing.csv", na.strings = c("", "NA", "#DIV/0!"))

summary(dataTrain)
summary(dataTest)
```

2. belt|arm|dumbbell|classe

```{r, eval=FALSE}
names(dataTrain)
BeltArmDumbell <- grepl(pattern = "belt|arm|dumbbell|classe", x = names(dataTrain))
accTrain <- dataTrain[, BeltArmDumbell]
accTest <- dataTest[, BeltArmDumbell]
```

3. Removing variables with NA's
```{r, eval=FALSE}
NAs <- rep(NA, length(names(accTrain))-1)
for(i in 1:length(NAs)){
      NAs[i] <- ifelse(sum(is.na(accTrain[, i])) != 0, TRUE, FALSE)
}

accTrain.na <- accTrain[, !NAs]
accTest.na <- accTest[, !NAs]

summary(accTrain.na)
```

4. Removing variables with near zero variance
```{r, eval=FALSE}
library(caret)

nzv.train <- nearZeroVar(x = accTrain.na, freqCut = 80/20, uniqueCut = 10, saveMetrics = TRUE, 
                         foreach = FALSE, allowParallel = TRUE)
accTrain.na.nzv <- accTrain.na[, !nzv.train[, "nzv"]]
accTest.na.nzv <- accTest.na[, !nzv.train[, "nzv"]]
```

## Creating fit
1. Partitioning data
```{r, eval=FALSE}
inTrain <- createDataPartition(y = accTrain.na.nzv$classe, p = 0.7, list = FALSE)

train <- accTrain.na.nzv[inTrain, ]
test <- accTrain.na.nzv[-inTrain, ]
validate <- accTest.na.nzv
```

2. Parallel computing + Model Creation

```{r, eval=FALSE}
library(doParallel)
library(randomForest)
registerDoParallel(cores=detectCores()-1)
system.time(RF <- foreach(ntree=rep(250, 4), .combine=combine, .packages='randomForest') %dopar%
                  randomForest(classe ~ ., ntree = ntree, data = train))
```

3. Assesing model
```{r, eval=FALSE}
predRF <- predict(RF, test)
confusionMatrix(test$classe, predRF)
```

4. Prediction on validate dataset
predRF.validate <- predict(RF, validate)

## Creating answers for COURSERA
```{r, eval=FALSE}
pml_write_files = function(x){
      n = length(x)
      for(i in 1:n){
            filename = paste0("problem_id_", i, ".txt")
            write.table(x[i], file=filename, quote=FALSE, row.names=FALSE, col.names=FALSE)
      }
}

pml_write_files(predRF.validate)
```






